\bf Nonparametric Bootstrap Kolmogorov-Smirnov Goodness-of-Fit Test for Marginal Distributions of Stationary Time Series

### 2024-02-19 manuscript/manuscript.tex
small manuscript changes

\subsection{Precipitation in Mansfield Connecticut}
\label{sec:precipitation}
Annual maximums of hourly precipitation in inches time series data were 
retrieved 
from the Chicago Midway International Airport (MDW), New York LaGuardia 
International 
Airport (LGA),
and Los Angeles International Airport (LAX) stations from the 
National Oceanic and Atmospheric Administration. These stations were selected 
from places of importance in the three largest American cities. LGA and
MDW were chosen over John F. Kennedy and O'Hare as more data was available
from these stations. The data for MDW is from
1948 to 2014, the data for LGA is from 1948 to 2013, and the
data for LAX is also from 1948 to 2013. We can apply our method to
the precipitation time series from each of these locations to test if they
follow the
Generalized Extreme Value (GEV) distribution using the \textsl{evd} 
package \citep{evd}. Precipitation maximum series 
typically do follow the GEV distribution, so we expect to fail to reject the
null hypothesis.

@@

The p-value is 0.71 for MDW, 0.13 for LGA, and 0.36 for LAX. Using a 
significance level as 
high as .10 still results in a failed rejection
of the null hypothesis for each of the three tests that the respective 
time series follow the GEV distribution.

@@

We expect the marginal distribution of Microsoft stock returns to have a 
slightly
heavier tail than the normal distribution. Using the \textsl{tseries} package 
\citep{tseries}, 
we gathered closing stock prices from January 1st, 1998 to December 31st, 2022.
Then we approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We tested that the stock returns are normally
distributed (which we expect to reject).  After that, we tested that the
marginal distribution of the time series follows the Student's $t$ distribution
with a fixed degrees of freedom.
While we 
could choose to estimate a fitted value of the degrees of freedom parameter $v$
as
part of our method, it is very difficult to do so. Therefore, we attempted to
test 
if it follows
the location-scale $t$ distribution with increasingly smaller specified degrees 
of freedoms. This was achieved with the \textsl{extraDistr} 
package \citep{extraDistr}. We
also observed how the method performs using increasingly smaller durations of
time. First, we tred the entire data set which has a duration of 25 years. Then,
we used the last 5 years of data: January 1st, 2018 to December 31st, 2022.
Finally, we tried the method only using the last year of data: January 1st, 2022
to December 31st, 2022.

@@

The p-values of our test when applied to Microsoft stock return data using
different settings are showcased in 
Tables~\ref{table:microsoft1}--\ref{table:microsoft2}.
We observe that when the duration of time is large, our method rejects the null
hypothesis unless the degrees of freedom specified is very precise. When
we use 25 years of data, the method
only fails to reject the null hypothesis at $\alpha = .05$ when 
the hypothesized $v = 2.2$, when 
the precision
is to the tenths place. For $\alpha = .10$, we only rail to reject the null 
hypothesis when the hypothesized $v = 2.15$, when the precision is to the 
hundredths place.
When using only 5 years of data, the method reaches a p-value of 
$0.05$ when the hypothesized $v = 2.5$, but the p-value is
lower for $v = 2.2$ and $v = 2.15$.
When we only use 1 year of data, the method fails to reject the null hypothesis
even when the hypothesized distribution family is normal ($v \to \infty$). The
p-value is maximized at 0.65 when we hypothesize that $v = 5$, but the p-value 
is lower for smaller values of $v$ when using only 1 year of data.

>>>>

\subsection{Precipitation in Mansfield Connecticut}
\label{sec:precipitation}
Annual maximums of hourly precipitation in inches time series data were 
retrieved 
from the Chicago Midway International Airport (MDW), New York LaGuardia 
International 
Airport (LGA),
and Los Angeles International Airport (LAX) stations from the 
National Oceanic and Atmospheric Administration. These stations were selected 
from places of importance in the three largest American cities. LGA and
MDW were chosen over John F. Kennedy and O'Hare as more data was available
from these stations. The data for MDW is from
1948 to 2014, the data for LGA is from 1948 to 2013, and the
data for LAX is also from 1948 to 2013. We can apply our method (as well
as the non-parametric bootstrap KS Test \citep{babu2004goodness} and
the parametric bootstrap KS Test) to
the precipitation time series from each of these locations to test if they
follow the
Generalized Extreme Value (GEV) distribution using the \textsl{evd} 
package \citep{evd}. Precipitation maximum series 
typically do follow the GEV distribution, so we expect to fail to reject the
null hypothesis.

@@

The p-value is 0.71 for MDW, 0.13 for LGA, and 0.36 for LAX when using our 
method.
When using Babu's non-parametric method which does not account for serial
dependence, the p-value is 0.74 for MDW, 0.19 for LGA, and 0.40 for LAX. 
When using the parametric bootstrap KS test, the p-value is 0.64 for MDW,
0.12 for LGA, and 0.35 for LAX. In this instance, the conclusions are the same 
(the three series follow the GEV distribution), but because of the difference
in p-values, it is possible for different conclusions to be found in another
study.

@@

We expect the marginal distribution of Microsoft stock returns to have a 
slightly
heavier tail than the normal distribution. Using the \textsl{tseries} package 
\citep{tseries}, 
we gathered closing stock prices from January 1st, 1998 to December 31st, 2022.
Then we approximated stock returns by taking the difference in the logarithm 
of the closing prices.
We tested that the stock returns are normally
distributed (which we expect to reject).  After that, we tested that the
marginal distribution of the time series follows the Student's $t$ distribution
with a fixed degrees of freedom.
While we 
could choose to estimate a fitted value of the degrees of freedom parameter $v$
as
part of our method, it is very difficult to do so. Therefore, we attempted to
test 
if it follows
the location-scale $t$ distribution with increasingly smaller specified degrees 
of freedoms. This was achieved with the \textsl{extraDistr} 
package \citep{extraDistr}. We
also observed how the method performs using increasingly smaller durations of
time. ,
we used the last 5 years of data: January 1st, 2018 to December 31st, 2022,
4 years of data: January 1st, 2019 to December 31st, 2022,
3 years of data: January 1st, 2020 to December 31st, 2022,
2 years of data: January 1st, 2021 to December 31st, 2022,
and 1 year of data: January 1st, 2022
to December 31st, 2022. In addition, we compared it to results from 
the Babu non-parametric and 
the parametric bootstrap KS Test.

@@

The p-values of our test when applied to Microsoft stock return data using
different settings are showcased in 
Tables~\ref{table:microsoft1}--\ref{table:microsoft2}. Although the p-values
are indeed different between the three methods, the conclusions at a .05 
significance 
level are mostly the same. This motivated an additional application on SP500
and SP100 data.
